---
title: "Data Import"
output: github_document
---

```{r setup}
library(tidyverse)
library(readxl) # read excel
library(haven) # read SAS
```

## Read in some data

Use relative path, not absolute path
bc absolute path only works on your computer
relative path: goes to


Read in the litters dataset.

startung at the "." and then goes to data file, then find the csv file
```{r}
litters_df = read_csv("./data/FAS_litters.csv")
#follow up step
#janitor:: --is to load the package janitor and to use the function...
#clean_names
#bc it is the only function that we will use in this practice
litters_df = janitor::clean_names(litters_df)
```


## Take a look at the data

Printing in the console

```{r}
litters_df
```

```{r}
#another way to check the dataset
#only to look at the first 6 rows
head(litters_df)
#check the last few rows
tail(litters_df)
```

```{r}
#we are not using library(skimr) bc we are only using the function skim()
skimr::skim(litters_df)
```

View(litters_df) is another way to check the data
but it is not very often used in RMD file
bc it opens up a new window, which doesn't function so good with the knit
so it is useful when using in console



## Options to read_csv

```{r}
litters_df = read_csv("./data/FAS_litters.csv", skip = 10, col_names = FALSE)
```


check out `?read_csv()` for more information


## Other file formats

Read in an excel file
```{r}
mlb_df = read_excel("./data/mlb11.xlsx")
mlb_df
```

Read in a SAS file.
```{r}
pulse_df = read_sas("./data/public_pulse_data.sas7bdat")
pulse_df
```

## Comparison with base R

what about `read.csv` ...?
read.csv is build-in function in base R
not recommended
```{r}
litters_base = read.csv("./data/FAS_litters.csv")
litters_readr = read_csv("./data/FAS_litters.csv")

litters_base #by default, it is printing the full dataset, translating some spaces to dots...
litters_readr # a bit easier to read
```



## Exporting data

Export the mlb sub-table

```{r}
write_csv(mlb_df, "./data/mlb_subtable.csv")
```








