---
title: "Data Import"
output: github_document
---

```{r setup}
library(tidyverse)
```

## Read in some data

Use relative path, not absolute path
bc absolute path only works on your computer
relative path: goes to


Read in the litters dataset.

startung at the "." and then goes to data file, then find the csv file
```{r}
litters_df = read_csv("./data/FAS_litters.csv")
#follow up step
#janitor:: --is to load the package janitor and to use the function...
#clean_names
#bc it is the only function that we will use in this practice
litters_df = janitor::clean_names(litters_df)
```


## Take a look at the data

Printing in the console

```{r}
litters_df
```

```{r}
#another way to check the dataset
#only to look at the first 6 rows
head(litters_df)
#check the last few rows
tail(litters_df)
```

```{r}
#we are not using library(skimr) bc we are only using the function skim()
skimr::skim(litters_df)
```

View(litters_df) is another way to check the data
but it is not very often used in RMD file
bc it opens up a new window, which doesn't function so good with the knit
so it is useful when using in console










